### 2020-03-17 thesis/pretext.tex
completed the pretext and acknowledgements.

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
presented on \underline{\jpsays{include the correct date here FORMAT = April 10, 2020!}}.
\vspace{1.0cm}

\justify{}
Title: \underline{\jpsays{Title of the thesis}}.
\vspace{2.0cm}

@@

\justify{}
\doublespacing
This work introduces the development of the novel flat-histogram Monte 
Carlo (MC) method SAD and explores the convergence properties of a 
variety of related weight-based MC methods. The new method is applied 
to a variety of physical `test' systems including the 2D Ising model, 
square-well fluid, and Lennard-Jones clusters. A driving motivation for 
developing novel Monte Carlo methods that have physically based tunable 
parameters is to provide simulation methods for exploring metal-organic 
frameworks (MOFs). A theoretical framework for gas adsorption and 
delivery in metal-organic frameworks is developed and compared with 
experimental data. SAD is a introduced as a powerful method for 
examining thermodynamic properties for MOFs.  A \emph{preliminary} 
groundwork is laid for the future development of 2D SAD which would be 
able to compute isotherms for any given MOF thereby providing a 
powerful way for researchers to determine a MOF's suitability for gas 
storage applications.

@@

\vspace*{4.0cm}
\begin{center}
$\copyright$ Copyright by Jordan K. Pommerenck \\
\jpsays{include the correct date here!} \\
(All Rights Reserved)
\end{center}

@@

\begin{center}
\jpsays{Title of the thesis}

\vspace{1.0cm}
by \\
Jordan K. Pommerenck \\
\vspace{3.0cm}
A DISSERTATION \\
\vspace{0.5cm}
submitted to \\
\vspace{0.5cm}
Oregon State University \\
\vspace{3.0cm}
in partial fulfillment of \\
the requirements for the \\
degree of \\
\vspace{1.0cm}
Doctor of Philosophy \\
\vspace{3.0cm}
Presented April 10, 2020  \\
Commencement June 2020 \jpsays{include the correct date here!}
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing
\justify{}
\underline{Doctor of Philosophy} dissertation of \underline{Jordan K. Pommerenck} presented on
\jpsays{get the date right here? April 10, 2015}. \\

@@

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
\jpsays{FIXME: "Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et
dolore magna aliqua. Ut}

>>>>

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
presented on April 30, 2020
\vspace{1.0cm}

\justify{}
Title: \underline{Advancing renewable gas storage using flat-histogram methods}.
\vspace{2.0cm}

@@

\justify{}
\doublespacing
This work introduces the development of the novel flat-histogram Monte
Carlo (MC) method SAD and explores the convergence properties of a
variety of related weight-based MC methods. The new method is applied
to a variety of physical ‘test’ systems including the 2D Ising model,
square-well fluid, and Lennard-Jones clusters. A driving motivation for
developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and
delivery in metal-organic frameworks is developed and compared with
experimental data. SAD is introduced as a powerful method for examining
thermodynamic properties for MOFs. A preliminary groundwork is laid for
the future development of a multi-dimensional SAD which would be able
to compute all isotherms for any given MOF thereby providing a powerful
way for researchers to determine a MOF’s suitability for gas storage
applications.

@@

\vspace*{4.0cm}
\begin{center}
$\copyright$ Copyright by Jordan K. Pommerenck \\
April 30, 2020 \\
(All Rights Reserved)
\end{center}

@@

\begin{center}
Advancing renewable gas storage using flat-histogram methods

\vspace{1.0cm}
by \\
Jordan K. Pommerenck \\
\vspace{3.0cm}
A DISSERTATION \\
\vspace{0.5cm}
submitted to \\
\vspace{0.5cm}
Oregon State University \\
\vspace{3.0cm}
in partial fulfillment of \\
the requirements for the \\
degree of \\
\vspace{1.0cm}
Doctor of Philosophy \\
\vspace{3.0cm}
Presented April 30, 2020  \\
Commencement June 2020
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing
\justify{}
\underline{Doctor of Philosophy} dissertation of \underline{Jordan K. Pommerenck} presented on
April 30, 2020. \\

@@

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
I gratefully acknowledge my graduate advisor David Roundy for his
constant support and guidance throughout my research. His breadth of knowledge
and hands-off approach have tremendously helped me to develop as a scientific
researcher.
I express thanks to my graduate committee members: David McIntyre, Davide Lazzati, Yun-Shik Lee, and GCR Chih-hung (Alex) Chang.
I would like to acknowledge the many outstanding graduate students that have positively impacted me (too many to name here but you know who you are).
I would like to acknowledge some of the outstanding undergraduate students
from our research lab that have worked on related research:
Tanner Simpson, Cade Trotter, and Christopher May.
Thank you all for your helpful discussions related to research and life in
general.
Finally, I would like to thank my parents for their unconditional support
throughout my PhD research.
